Financial markets for reaching ``green" targets: Cap-and-trade strategies in the Chilean electricity sector

### 2020-04-20 draft_paper/draft_v1.tex
acentos bibliografía
avances previos 20 abril gráfico calibración

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[gen]{eurosym}
%\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage[stable]{footmisc}
\usepackage{caption}
\usepackage{subcaption} 
\usepackage[title]{appendix}
\usepackage{multirow}
%\usepackage{xcolor}
\usepackage[margin=1.0in]{geometry}
\usepackage{array}
\usepackage[title]{appendix}
\usepackage{threeparttable}
%\usepackage[numbers,sort&compress]{natbib}

@@

%\smallskip
%A capacity investment model is characterized by
%\small
%$$\left(\left((a_i,b_i),I_i, TC_i(t,\omega),TCR_i(t,\omega), CF_i, \bar{Q}_i, RP_i,\varepsilon_i\right)_{i\in\{1,...N\}},\tau,D, (Pr(\omega))_{\omega\in\Omega}\right)\in\Xi^N\times\mathbb{R}_+\times\left(\mathbb{R}_+\times\mathbb{R}_+^{T\times\Omega}\right)\times\Delta.$$
%\normalsize

@@

\begin{figure}[ht!]
 \includegraphics[width=\textwidth]{draft_paper/Figures/figure1.png}
 \caption{Panel (a): Production levels for each technology in 2018 obtained from the calibration of our model. Panel (b): Production levels per technology in the period 2019-2050 for our base-case scenario in our model, that is, business-as-usual, no green policies planned or implemented. }
  \label{fig:bc}
  \end{figure}

@@

\begin{table}[!htbp]
\centering
  \begin{threeparttable}[t]
       \begin{tabular}{ c c c c } 
\hline
 & Technology & Base Case Roadmap 2050 & This work \\
\hline
\multirow{4}{8em}{Energy Production (\%)} & NCRE\tnote{a} & 22\%-67\% & 36.5\% \\ 
 & Hidro generation & 24\%-32\% & 18\% \\ 
& Thermal generation & 9\%-46\% & 45.5\% \\
\hline
%\multicolumn{3}{l}{\footnotetext{According to Chile's Energy Policies document, NCRE are Solar Photovoltaic and Concentrated Solar Power (CSP), Geothermal and Wind }} \\
\end{tabular}
     \begin{tablenotes}
     \footnotesize{
     \item[a] According to Chile's Energy Policies document, NCRE are Solar Photovoltaic and Concentrated Solar Power (CSP), Geothermal and Wind .
     }
   \end{tablenotes}
    \end{threeparttable}%
    \caption{Energy Generation from our model compared with Chile's Energy Policies projections for the year 2050}
  \label{tab:bc_comp}%
\end{table}%

>>>>

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[gen]{eurosym}
%\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage[stable]{footmisc}
\usepackage{caption}
\usepackage{subcaption} 
\usepackage[title]{appendix}
\usepackage{multirow}
%\usepackage{xcolor}
\usepackage[margin=1.0in]{geometry}
\usepackage{array}
\usepackage[title]{appendix}
\usepackage{threeparttable}
%\usepackage[numbers,sort&compress]{natbib}

@@

@@

\begin{figure}[ht!]
 \includegraphics[width=\textwidth]{draft_paper/Figures/Figure1_comp.png}
 \caption{\color{red}Panel (a): The outer ring shows the production percentage over the total electricity production in 2018 for each technology  obtained from the calibration of our model. The inner ring shows the real operation data for that year. Panel (b): Production levels per technology in the period 2019-2050 for our base-case scenario in our model, that is, business-as-usual, no green policies planned or implemented. }
  \label{fig:bc}
  \end{figure}

@@

\begin{table}[!htbp]
\centering
  \begin{threeparttable}[t]
       \begin{tabular}{ c c c c } 
\hline
 & Technology & Base Case Roadmap 2050 & This work \\
\hline
\multirow{4}{8em}{Energy Production (\%)} & NCRE\tnote{a} & 22\%-67\% & 36.5\% \\ 
 & Hydro generation & 24\%-32\% & 18\% \\ 
& Thermal generation & 9\%-46\% & 45.5\% \\
\hline
%\multicolumn{3}{l}{\footnotetext{According to Chile's Energy Policies document, NCRE are Solar Photovoltaic and Concentrated Solar Power (CSP), Geothermal and Wind }} \\
\end{tabular}
     \begin{tablenotes}
     \footnotesize{
     \item[a] According to Chile's Energy Policies document, NCRE are Solar Photovoltaic and Concentrated Solar Power (CSP), Geothermal and Wind .
     }
   \end{tablenotes}
    \end{threeparttable}%
    \caption{Energy Generation from our model compared with Chile's Energy Policies projections for the year 2050}
  \label{tab:bc_comp}%
\end{table}%
